Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-14 report/report.tex
Update todo
Include introduction disposition points from meeting log

Description of a virtual city and its contents.

@@

Description of procedural modelling of cities (find reference).

@@

Additionally, the topic is of interest for 3D content creators in for example the fields of video game design or 3D animation. A trend in these fields is using methods of procedural modeling to create large amounts of 3D content quickly and efficiently, while requiring as little hand modeling as possible. Studios who create large worlds are often interested in solutions that generate large road networks without any hand modeling.
Navigation agents, they might fail navigating when faced with a too narrow path or intersecting obstacles
Using a road network to creates an underlying navmesh

@@

% Thursday:
% TODO: Fix citings like they appear in the example thesis

% TODO: Introduction disposition (See meeting log for suggestions)
    % TODO: Introduction, picture of a virtual city
    % TODO: Main challenge: How to reconstruct a 3D city. Make this more clear in the abstract
    % TODO: 2.1: Add a sentence about where the question fits into the big picture
% TODO: Collision study implementation, disposition
    % TODO: Figure detailing the steps in the point-matching algorithm
    % TODO: Edge distance algorithm, outline, algorithm + picture

>>>>

Picture of a virtual city.

Description of a virtual city and its contents.
Consisting of road network, buildings, details.
Roads have different types.

@@

Description of procedural modelling of cities (find reference).
Importing geodata from online databases and converting it to a 3D city representation.

At the base of this process is the procedural layout of road networks in 3D.

@@

Additionally, the topic is of interest for 3D content creators in for example the fields of video game design or 3D animation. A trend in these fields is using methods of procedural modeling to create large amounts of 3D content quickly and efficiently, while requiring as little hand modeling as possible. Studios who create large worlds are often interested in solutions that generate large road networks without any hand modeling.
%TODO: (Parish Müller: Procedural modelin of cities)

@@

% Thursday:
% TODO: Fix citings like they appear in the example thesis
% TODO: Collision study implementation, disposition
    % TODO: Figure detailing the steps in the point-matching algorithm
    % TODO: Edge distance algorithm, outline, algorithm + picture
